---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(osrmr)
```

## osrmr

osrmr is a wrapper around the OSRM API (https://github.com/Project-OSRM/osrm-backend/blob/master/docs/http.md).
osrmr works with API versions 4 and 5 and can handle servers that run locally as well as the osrm webserver.


## Installation

You can install osrmr from `CRAN` or `github` with:

```{r, c01, eval = FALSE}
install.packages("osrmr")

# install.packages("devtools")
devtools::install_github("ims-fhs/osrmr")
```



## Examples

Access the OSRM with R using the onlinehost (webserver) of OSRM to: 

 * generate coordinates from given coordinates, which are accessible by car with `nearest()`
 * calculate waytimes and more for specific routes from start- to end-destination with `viaroute()`
 * decode polylines using a polyline-specific precision with `decode_geom()`

```{r, c02, eval = TRUE}
library(osrmr)
nearest(lat = 47, lng = 8, api_version = 5, localhost = FALSE)
viaroute(lat1 = 47.1, lng1 = 8.1, lat2 = 46.9, lng2 = 8.3, instructions = FALSE,
         api_version = 5, localhost = FALSE)

encoded_polyline_precision_5 <- rjson::fromJSON(file = "http://router.project-osrm.org/route/v1/driving/8.0997,47.1002;8.101110,47.10430?steps=false&geometries=polyline")$routes[[1]]$geometry
decode_geom(encoded_polyline_precision_5, precision = 5)

```

For more detailed Information about the components of the osrmr package, check out the vignette. 

